A Finite Volume Formulation for the 2D Incompressible Navier-Stokes and Conduction Equations

### 2012-07-22 doc/model_problems/model_problems.tex
Adding thesis proposal document.

%        File: model_problems.tex
%
\documentclass[letterpaper,12pt]{article}
\usepackage[top=1.0in,bottom=1.0in,left=1.0in,right=1.0in]{geometry}
\usepackage{verbatim}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage[usenames]{color}
\usepackage[
naturalnames = true, 
colorlinks = true, 
linkcolor = black,
anchorcolor = black,
citecolor = black,
menucolor = black,
urlcolor = blue
]{hyperref}

@@

where $C_P$ is the specific heat capacity of the material. We also
define the heat flux using Fick's law:

@@

Here we balance the change in energy in the unit cell over a unit of
time with the flux on the cell boundaries. Inserting
Eq.~(\ref{eq:conduction_energy}) int
Eq.~(\ref{eq:conduction_conservation}) and dividing by the cell volume
recovers the cell averaged temperature and specific heat on the left
hand side:

@@

We then insert Eq.~(\ref{eq:conduction_ficks_law}), difference the
left hand side, and integrate the right hand side over a unit time
step, maintaining the conservation properties of the system:

\begin{equation}
  C_{P_{ij}} ( T^{n+1}_{ij} - T^n_{ij} ) = \frac{1}{\Delta_i \Delta_j}
  \int_{t^n}^{t^{n+1}} [ -\beta_{i-1/2,j} \nabla T_{i-1/2,j} +
    \beta_{i+1/2,j} \nabla T_{i+1/2,j} - \beta_{i,j-1/2} \nabla
    T_{i,j-1/2} +\beta_{i,j+1/2} \nabla T_{i,j+1/2} ] dt\:.
  \label{eq:conduction_time_integral}
\end{equation}

@@

\begin{equation}
  C_{P_{ij}}( T^{n+1}_{ij} - T^n_{ij} ) = \frac{\Delta_t}{\Delta_i
    \Delta_j} -\beta_{i-1/2,j} \frac{T^{n+1}_{ij}
    -T^{n+1}_{i-1,j}}{\Delta_i} +\beta_{i+1/2,j} \frac{T^{n+1}_{i+1,j}
    -T^{n+1}_{ij}}{\Delta_i} -\beta_{i,j-1/2} \frac{T^{n+1}_{ij}
    -T^{n+1}_{i,j-1}}{\Delta_j} +\beta_{i,j+1/2} \frac{T^{n+1}_{i,j+1}
    -T^{n+1}_{i,j-1}}{\Delta_j}
  \label{eq:conduction_fv_equation}
\end{equation}

@@

@@

>>>>

%        File: model_problems.tex
%
\documentclass[letterpaper,12pt]{article}
\usepackage[top=1.0in,bottom=1.0in,left=1.25in,right=1.25in]{geometry}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{tmadd,tmath}
\usepackage[mathcal]{euscript}
\usepackage[usenames]{color}
\usepackage[
naturalnames = true, 
colorlinks = true, 
linkcolor = black,
anchorcolor = black,
citecolor = black,
menucolor = black,
urlcolor = blue
]{hyperref}

@@

where $C_P$ is the specific heat capacity of the material. We also
define the heat flux, $F$, in terms of temperature using Fick's law:

@@

Here we balance the time rate of change in energy in the unit cell
with the flux on the cell boundaries. Inserting
Eq.~(\ref{eq:conduction_energy}) int
Eq.~(\ref{eq:conduction_conservation}) and dividing by the cell volume
recovers the cell averaged temperature and specific heat on the left
hand side:

@@

We then insert Eq.~(\ref{eq:conduction_ficks_law}), difference the
left hand side, and integrate, maintaining the conservation properties
of the system:

\begin{multline}
  C_{P_{ij}} ( T^{n+1}_{ij} - T^n_{ij} ) = \frac{1}{\Delta_i \Delta_j}
  \int_{t^n}^{t^{n+1}} [ -\beta_{i-1/2,j} \nabla T_{i-1/2,j}\\
    + \beta_{i+1/2,j} \nabla T_{i+1/2,j} - \beta_{i,j-1/2} \nabla
    T_{i,j-1/2} +\beta_{i,j+1/2} \nabla T_{i,j+1/2} ] dt\:.
  \label{eq:conduction_time_integral}
\end{multline}

@@

\begin{multline}
  C_{P_{ij}}( T^{n+1}_{ij} - T^n_{ij} ) = \frac{\Delta_t}{\Delta_i
    \Delta_j} -\beta_{i-1/2,j} \frac{T^{n+1}_{ij}
    -T^{n+1}_{i-1,j}}{\Delta_i} +\beta_{i+1/2,j} \frac{T^{n+1}_{i+1,j}
    -T^{n+1}_{ij}}{\Delta_i}\\
  -\beta_{i,j-1/2} \frac{T^{n+1}_{ij}
    -T^{n+1}_{i,j-1}}{\Delta_j} +\beta_{i,j+1/2} \frac{T^{n+1}_{i,j+1}
    -T^{n+1}_{i,j-1}}{\Delta_j}\:.
  \label{eq:conduction_fv_multline}
\end{multline}

We will define $\alpha$ as:

\begin{equation}
  \alpha_{ij} = \frac{\Delta_t}{C_{P_{ij}} \Delta_i \Delta_j}
  \label{eq:conduction_coeff}\:.
\end{equation}

Rearranging for temperature, we can then form a system of equations
amenable to matrix solutions, not yet considering boundary conditions,
arriving at the discrete, time-dependent conduction equation:

\begin{multline}
 \Big[1 + \frac{\alpha_{ij}}{\Delta_i}(\beta_{i-1/2,j} + \beta_{i+1/2,j})\Big]
 T^{n+1}_{ij} + \Big[-\frac{\alpha_{ij}}{\Delta_i} \beta_{i-1/2,j}\Big]
 T^{n+1}_{i-1,j} + \Big[\frac{-\alpha_{ij}}{\Delta_i} \beta_{i+1/2,j}\Big]
 T^{n+1}_{i+1,j}\\
 + \Big[-\frac{\alpha_{ij}}{\Delta_j} \beta_{i-1/2,j}\Big]
 T^{n+1}_{i,j-1} + \Big[-\frac{\alpha_{ij}}{\Delta_j} \beta_{i+1/2,j}\Big]
 T^{n+1}_{i,j+1} = T^n_{ij}\:.
 \label{eq:conduction_inner_terms}
\end{multline}

@@

We will consider both Neumann and Dirichlet type boundary conditions
for the conduction equation. For the Neumann condition we have a
constant temperature at the boundary:

\begin{equation}
  T_{ij} = T_0, \forall (i,j) \in \Gamma
  \label{eq:conduction_neumann}
\end{equation}

For the Dirichlet condition, we have a constant heat flux at the boundary.

\subsection{Linear System Form}

@@

\subsection{Nonlinear System Form}
